Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-08-28 analysis/presentation/sim_survey_presentation.Rmd
Describe survey portion of the simulation in the presentation

## wrapper for layout with some different defaults for this slideshow
tight_layout <- function(p, 
                         plot_bgcolor = "transparent",
                         paper_bgcolor = "transparent",
                         margin = list(l = 0, r = 0, t = 0, b = 0, pad = 0),
                         font = list(size = 14), ..., data = NULL) {
  layout(p, plot_bgcolor = plot_bgcolor, paper_bgcolor = paper_bgcolor,
         margin = margin, font = font, ..., data = data)
}

@@

@@

- Try and figure out the bug that prevents the plotly plots from working in this part of the slideshow (alternate fix to containing it in a device)
- Figure out how to use the Google Font with plotly
- Set-up global layout arguents somehow
- Figure out how to make a sub-title for a slide below main title
- Reverse color ramp in grid figure
- Frame by year for spatial abundance plot (consider fixing one year, animate age / fix age and animate year)

## References

>>>>

## wrapper for layout with some different defaults for this slideshow
tight_layout <- function(p, 
                         plot_bgcolor = "transparent",
                         paper_bgcolor = "transparent",
                         margin = list(l = 0, r = 0, t = 0, b = 0, pad = 0),
                         font = list(size = 14, family = "'Montserrat', sans-serif"), 
                         ..., data = NULL) {
  layout(p, plot_bgcolor = plot_bgcolor, paper_bgcolor = paper_bgcolor,
         margin = margin, font = font, ..., data = data)
}

@@

## Simulate survey

- Split grid into $N_{div}$ divisions and $N_{strat}$ depth-based strata
- Set allocation defined by specifying set density, $D_{sets}$
- Binomial sampling was used to simulate catch:
    - $n_{a,y,s} \sim Bin(N_{a,y,s}, \frac{A_{trawl}}{A_{cell}} q_a )$
    - Accounts for trawl size relative to cell size, $\frac{A_{trawl}}{A_{cell}}$, and catchability, $q_a$ (controled using a logistic curve)

## Simulate survey

- Lengths simulated using the original von Bertalanffy growth curve [@Cailliet2006]:
    - $log(l) = log(l_{\infty} - (l_{\infty} - l_0) e^{-Ka}) + \varepsilon$, where $\varepsilon \sim N(0, \sigma_{l}^2)$
- Sub-sampling is then conducted
    - A maximum number of lengths are measured per set, $M_{lengths}$
    - A maximum number of ages, $M_{ages}$, are sampled per length group, $l_{group}$, per division

## Simulate survey {.tighter}

### Catch in year 1 survey simulation 1

<dev class = "left">
```{r}
plot_samp_dist(sim) %>% 
  tight_layout(margin = list(l = 0, r = 0, t = 0, b = 40, pad = 0))
```
</dev>

## Acknowledgements

- Todo

@@

- Try and figure out the bug that prevents the plotly plots from working in this part of the slideshow (alternate fix to containing it in a device)

## References {.smaller}
